```{r, include=FALSE}
library(ggplot2)
```



Question
========
In *Think Bayes* stellt Allen Downey folgende Aufgabe:

"Suppose there are two bowls of cookies.

Bowl 1 contains 30 vanilla cookies and 10 chocolate cookies.

Bowl 2 contains 20 vanilla cookies and 20 chocolate cookies.

Now suppose you choose one of the bowls at random and, without looking, choose a cookie at random.

*If the cookie is vanilla, what is the probability that it came from Bowl 1?*"

```{r}
#| echo: false
#| eval: false
#| fig-cap: "Zwei Keksdosen"
jar_data <- data.frame(
  x_min = c(1, 4),
  x_max = c(2.5, 5.5),
  y_min = c(0, 0),
  y_max = c(3, 3),
  color = c("blue", "green")
)

ggplot() +
  geom_rect(data = jar_data, aes(xmin = x_min, xmax = x_max, ymin = y_min, ymax = y_max, fill = color),
            color = "black") +
  scale_fill_identity() +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  xlim(0, 7) +
  ylim(0, 4)
```


*Wählen Sie die korrekte Antwort!*

Answerlist
----------
* .60
* .40
* .75
* .33
* .50


Solution
========
```{r}
#| message: false
library(tidyverse)

d <-
  tibble(
    p_Gitter = c(1, 2),
    Priori  = .5) %>%
    mutate(
      Likelihood = c(3/4, 2/4),
      unstd_Post = Likelihood * Priori,
      Post = unstd_Post / sum(unstd_Post))

d %>%
  knitr::kable(digits=2)
```

Die Antwort lautet **.60**. Es ist übrigens egal, ob Sie für die Priori-Werte .5 oder 1 (oder eine andere Zahl) wählen, solange Sie für alle Hypothesen die gleiche Zahl verwenden – das Ergebnis bleibt gleich.


Answerlist
----------
* True
* False
* False
* False
* False


Meta-information
================
exname: kekse01-schoice
extype: schoice
exsolution: 10000
exshuffle: 5
